---
title: "607 Week8 Project3"
author: "Stephanie Roark, Mike Groysman, Zach Herold, and Chad Bailey"
date: "October 19, 2018"
---

##Overview

This project is an opportunity to practice both the hard technical skills around R and SQL as well as the soft skills of distance collaboration with classmates. The primary question of this project is: Which are the most valued data science skills? Groups are to seek an answer to this question while also completing each of the following:

* Form a group of 3-5 members
* Establish the tools the group will use to collaborate
* Determine what data to collect and how to load it
* Use R to tidy and transform the data
* Load the data into a relational database as a set of normalized tables
* Use R to perform exploritory analysis (and any additional transformations needed)
* Provide documentation of data sources, transformation, analysis, and results
* Create a 3-5 minute presentation around the project
* Submit all code, documentation, presentation, and links to collaboration spaces

## <Insert other documentation>

Load the selected data sources
```{r}
file_location_1 <- 'https://raw.githubusercontent.com/ZacharyHerold/CUNY-DATA607/master/SCData.csv'
ds_user_profiles_skills <- read.table(file_location_1, sep = ",", header = TRUE, stringsAsFactors = FALSE)


file_location_2 <- 'https://raw.githubusercontent.com/ZacharyHerold/CUNY-DATA607/master/ds_general_skills_revised.csv'
ds_job_postings_skills <- read.table(file_location_2, sep = ",", header = TRUE, stringsAsFactors = FALSE)


file_location_3 <- 'https://raw.githubusercontent.com/ZacharyHerold/CUNY-DATA607/master/ds_job_listing_software.csv'
ds_job_postings_software <- read.table(file_location_3, sep = ",", header = TRUE, fill = TRUE, stringsAsFactors = FALSE)
```

Tidy and transform the data
```{r message=FALSE}
library(dplyr)
library(tidyr)
library(Hmisc)

#ds_user_profiles_skills: 
    #done to standardize across tabls to allow joining
    ds_user_profiles_skills$Skill <- tolower(ds_user_profiles_skills$Skill)
    ds_user_profiles_skills$Skill <- capitalize(ds_user_profiles_skills$Skill)
    
    #split off user profile software
    ds_user_profiles_software <- ds_user_profiles_skills %>%
      filter(Skill %in% c("R"
                          ,"Python"
                          ,"Sql"
                          ,"Matlab"
                          ,"Java"
                          ,"C++"
                          ,"Sas"
                          ,"Hadoop"))
    
    #split off user profile software
    ds_user_profiles_skills <- ds_user_profiles_skills %>%
      filter(!Skill %in% c("R"
                          ,"Python"
                          ,"Sql"
                          ,"Matlab"
                          ,"Java"
                          ,"C++"
                          ,"Sas"
                          ,"Hadoop"))

    
#ds_job_postings_skills: 
    #limit to desired rows
    ds_job_postings_skills <- ds_job_postings_skills[c(1:15, 17),]
    
    #cleanup
    ds_job_postings_skills <- ds_job_postings_skills %>%
      mutate(Skill_Type = "General Skill")  %>%
      rename(Skill = "Keyword") %>%
      select("Skill_Type", "Skill", "LinkedIn", "Indeed", "SimplyHired", "Monster")
    
    #transform to "normalized" structure
    ds_job_postings_skills <-gather(ds_job_postings_skills, "Site", "N_Records", 3:6)

    #done to standardize across tables to allow joining to other tables
    ds_job_postings_skills$Skill <- tolower(ds_job_postings_skills$Skill)
    ds_job_postings_skills$Skill <- capitalize(ds_job_postings_skills$Skill)

    
#ds_job_postings_software:
    #limit to desired rows
    ds_job_postings_software <- ds_job_postings_software[c(1:37, 39),]
    
    #cleanup
    ds_job_postings_software <- ds_job_postings_software %>%
      mutate(Skill_Type = "Software/Language Skill") %>%
      rename(Skill = "Keyword") %>%
      select("Skill_Type", "Skill", "LinkedIn", "Indeed", "SimplyHired", "Monster")
      
    #transform to "normalized" structure
    ds_job_postings_software <-gather(ds_job_postings_software, "Site", "N_Records", 3:6)

    #done to standardize across tabls to allow joining to other tables
    ds_job_postings_software$Skill <- tolower(ds_job_postings_software$Skill)
    ds_job_postings_software$Skill <- capitalize(ds_job_postings_software$Skill)



ds_user_profiles_skills
ds_user_profiles_software
ds_job_postings_skills
ds_job_postings_software




```