---
title: "607 Week8 Project3"
author: "Stephanie Roark, Mike Groysman, Zach Herold, and Chad Bailey"
date: "October 19, 2018"
---

##Overview

This project is an opportunity to practice both the hard technical skills around R and SQL as well as the soft skills of distance collaboration with classmates. The primary question of this project is: Which are the most valued data science skills? Groups are to seek an answer to this question while also completing each of the following:

* Form a group of 3-5 members
* Establish the tools the group will use to collaborate
* Determine what data to collect and how to load it
* Use R to tidy and transform the data
* Load the data into a relational database as a set of normalized tables
* Use R to perform exploritory analysis (and any additional transformations needed)
* Provide documentation of data sources, transformation, analysis, and results
* Create a 3-5 minute presentation around the project
* Submit all code, documentation, presentation, and links to collaboration spaces

## <Insert other documentation>

Load the selected data sources
```{r}
file_location_1 <- 'https://raw.githubusercontent.com/ZacharyHerold/CUNY-DATA607/master/SCData.csv'
ds_user_profiles_skills <- read.table(file_location_1, sep = ",", header = TRUE, stringsAsFactors = FALSE)


file_location_2 <- 'https://raw.githubusercontent.com/ZacharyHerold/CUNY-DATA607/master/ds_general_skills_revised.csv'
ds_job_postings_skills <- read.table(file_location_2, sep = ",", header = TRUE, stringsAsFactors = FALSE)


file_location_3 <- 'https://raw.githubusercontent.com/ZacharyHerold/CUNY-DATA607/master/ds_job_listing_software.csv'
ds_job_postings_software <- read.table(file_location_3, sep = ",", header = TRUE, fill = TRUE, stringsAsFactors = FALSE, strip.white = TRUE, comment.char = "")

```

Tidy and transform the data
```{r message=FALSE}

#load the necessary supporting packages
library(stringr)
library(dplyr)
library(tidyr)
library(Hmisc)
library(ggplot2)

#ds_user_profiles_skills: 
    ds_user_profiles <- ds_user_profiles_skills %>%
      mutate(Skill = tolower(Skill)) %>%
      mutate(Skill = capitalize(Skill)) %>%
      mutate(Skill_Type = ifelse(Skill %in% c("R"
                                              ,"Python"
                                              ,"Sql"
                                              ,"Matlab"
                                              ,"Java"
                                              ,"C++"
                                              ,"Sas"
                                              ,"Hadoop")
                                 ,"Software/Language Skill"
                                 ,"General Skill")) %>%
      select("Skill_Type", "Skill", "Percentage")
      
      
 
#ds_job_postings_n_postings
    #pull out the total number of postings (to be used later)
    ds_jp_n_postings <- ds_job_postings_software[c(41),]
    
    ds_jp_n_postings <- ds_jp_n_postings %>%
      select("LinkedIn"
             , "Indeed"
             , "SimplyHired"
             , "Monster")
    
    ds_jp_n_postings <- gather(ds_jp_n_postings, "Site", "N_Postings", 1:4)
    ds_jp_n_postings <- ds_jp_n_postings %>%
      mutate(N_Postings = str_replace_all(N_Postings, ",", "")) %>%
      mutate(N_Postings = as.numeric(N_Postings))
    ds_jp_n_postings
    
       
#ds_job_postings_skills: 
    #limit to desired rows
    ds_job_postings_skills <- ds_job_postings_skills[c(1:15, 17),]
    
    #cleanup
    ds_job_postings_skills <- ds_job_postings_skills %>%
      mutate(Skill_Type = "General Skill")  %>%
      select("Skill_Type"
             , "Keyword"
             , "LinkedIn"
             , "Indeed"
             , "SimplyHired"
             , "Monster")
 
    
#ds_job_postings_software:
    
    #limit to desired rows
    ds_job_postings_software <- ds_job_postings_software[c(1:37, 39),]
    
    #cleanup
    ds_job_postings_software <- ds_job_postings_software %>%
      #filter(c(1:37)) %>%
      mutate(Skill_Type = "Software/Language Skill") %>%
      select("Skill_Type"
             , "Keyword"
             , "LinkedIn"
             , "Indeed"
             , "SimplyHired"
             , "Monster")

# union (append) the two job posting datasets
    ds_job_postings <- union(ds_job_postings_skills
                             ,ds_job_postings_software)
              
#tidy the unioned job postings dataset
    ds_job_postings <- ds_job_postings %>%
      rename(Skill = "Keyword") %>%
      filter(Skill != "Total") %>%
      mutate(Skill = tolower(Skill)) %>%
      mutate(Skill = capitalize(Skill)) 
    
#transform to "normalized" structure
    ds_job_postings <-gather(ds_job_postings, "Site", "N_Records", 3:6)
    
#cast to numeric
    ds_job_postings <- ds_job_postings %>%
      mutate(N_Records = str_replace_all(N_Records, ",", "")) %>%
      
      filter(!is.na(N_Records)) %>%
      filter(N_Records != "") %>%
      mutate(N_Records = as.numeric(N_Records))
```


Add percent of job postings listing that skill
```{r}
ds_job_postings <- inner_join(ds_job_postings
                              , ds_jp_n_postings
                              , by = "Site")

ds_job_postings <- ds_job_postings %>%
  mutate(Pct_Postings = round(N_Records/N_Postings*100, 2)) %>%
  select(-N_Postings)
 
head(ds_job_postings, n=10)
```

Pull the top skills (listed >50% of postings) across sites
```{r}
jp_avg_across_sites <- ds_job_postings %>%
  group_by(Skill_Type, Skill) %>%
  summarise(Avg_Pct_Postings = mean(Pct_Postings)) %>%
  arrange(desc(Avg_Pct_Postings)) %>%
  filter(Avg_Pct_Postings >= 50)

jp_avg_across_sites <- as.data.frame(jp_avg_across_sites)
jp_avg_across_sites
```

Pull the top skills (listed >50% of postings) across sites  
Also, review the frequency across sites and the order within sites
```{r}
jp_avg_within_sites <- ds_job_postings %>%
  group_by(Site, Skill_Type, Skill) %>%
  summarise(Avg_Pct_Postings = mean(Pct_Postings)) %>%
  arrange(Site, desc(Avg_Pct_Postings)) %>%
  filter(Avg_Pct_Postings >= 50)

jp_avg_within_sites <- as.data.frame(jp_avg_within_sites)
jp_avg_within_sites
```

Compare that to the top skills listed by data scientists
```{r}

ds_user_profiles %>%
  arrange(desc(Percentage))





```